Late Pleistocene stone artefact technology at Mau A, Yen Bai, Northern Vietnam

### 2022-03-25 analysis/paper/paper.Rmd
Merged the environmental context section with the broader introduction section and added more text and citations

## Introduction
<!-- BM: In this section we need to review in very precise detail, previous work on investigating flake shape and identifying what affects flake shape, especially the Borel papers, not just in Southeast Asia, but anywhere in the world, Look in Borel to see what papers they cite, and we should summarise the most relevant of those, e.g. the previous papers that are most similar to our project  -->

@@

## Paleoenvironmental and Archaeological Context
<!-- also make sure to provide a general context of paleolithic southeast asia. See previously suggested papers and look at context papers cited by Borel et al.  -->

While early hominins reached Mainland Southeast Asia as early as 800 ka ago (Forestier et al., 2022), the oldest skeletal remains of anatomically modern humans date to roughly 50-70 ka ago (Demeter et al., 2017; Shackelford et al., 2018).

Mainland Southeast Asia 
-Further context from (McAdams et al., 2020)

Here is a citation [@Marwick2017]

## Excavations at Mau A

@@

>>>>

## Introduction
<!-- BM: In this section we need to review in very precise detail, previous work on investigating flake shape and identifying what affects flake shape, especially the Borel papers, not just in Southeast Asia, but anywhere in the world, Look in Borel to see what papers they cite, and we should summarise the most relevant of those, e.g. the previous papers that are most similar to our project  -->
<!-- also make sure to provide a general context of paleolithic southeast asia. See previously suggested papers and look at context papers cited by Borel et al.  -->

While early hominins reached Mainland Southeast Asia as early as 800 ka ago (Forestier et al., 2022), the oldest skeletal remains of anatomically modern humans date to roughly 50-70 ka ago (Demeter et al., 2017; Shackelford et al., 2018). MIS 2 in Northern Vietnam was characterized by sporadic human occupation of caves, localized differences in climate (with shifting cover of rain forest between the moist highlands and the variable lowlands) and the accumulation of mollusk shell middens (McAdams et al., 2020; McAdams et al., 2022). Humans in Mainland Southeast Asia (from now on MSEA) would repeatedly reuse caves, accumulating numerous layers of discarded shells, ash, and lithics over multiple periods of occupation, with intervening periods of abandonment and occupation by faunal species such as bats (McAdams et al., 2020).

@@

<!-- saving this for later:  Here is a citation [@Marwick2017]  -->
## Excavations at Mau A

@@

McAdams, C., Morley, M. W., Fu, X., Kandyba, A. V., Derevianko, A. P., Nguyen, D. T., Doi, N. G., & Roberts, R. G. (2022). Late Pleistocene shell midden microstratigraphy indicates a complex history of human–environment interactions in the uplands of northern Vietnam. Philosophical Transactions of the Royal Society B: Biological Sciences, 377(1849), 20200493. https://doi.org/10.1098/rstb.2020.0493
